---
title: "pricegal"
author: "Leandro Jimenez"
date: "Sunday2016"
output: ioslides_presentation
runtime: shiny
---



Course Project: Shiny Application and Reproducible Pitch
========================================================
author: leandro
date: 2016




Overview
========================================================

This was built as part of a deliverable for the course **Developing Data Products** as part of the Coursera Data Science Specialization.


Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/jleandroj/pricegal 

take at look in the aplications https://jleandroj.shinyapps.io/pricegal/




read
========================================================

Money that you need to spend for your trip

providing details: like distance, price (gasoline) and gas.After choosing cyl(Cylinders), Disp(Displacement) and hp(Horse Power).

getting a table with results.





MTCARS Dataset
========================================================

The data used was mtcars dataset. this a head of 5 first results: 

```{r, echo=FALSE,warning=FALSE}
head(mtcars,n=5)
```


Plot
========================================================

cyl and displacement or mpg 
```{r, echo=FALSE,warning=FALSE}
library(car)
scatterplot.matrix(~disp+cyl+mpg, data=mtcars)
```
